Viscous Transport in Eroding Porous Media

### 2019-06-12 docs/transport/erosion_transport.tex
do the result section in transport paper

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighbor tracers have been
seperated by the bodies. 
}

@@

\begin{figure}[H]
%\begin{subfigure}[b]{0.5\textwidth}
\center
\includegraphics*[width =0.5\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}%
%\begin{subfigure}[b]{0.5\textwidth}
%\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}
\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of U verse time.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256 $}
\end{center}
\end{figure}

@@

}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The historical trajectories of 
200 tracers released at x = -1 in the fluid with multiple bodies}
\end{center}
\end{figure}

>>>>

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
}

@@

\begin{figure}[H]
%\begin{subfigure}[b]{0.5\textwidth}
\center
\includegraphics*[width =0.5\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}%
%\begin{subfigure}[b]{0.5\textwidth}
%\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}
\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of $U$ in log scale verse time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256$.}
\end{center}
\end{figure}

@@

}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The historical trajectories of 
200 tracers released at x = -1 in the fluid with multiple bodies.}
\end{center}
\end{figure}
